---
title: "p8105_hw1_qy2234"
author: "Michael Yan"
date: "9/13/2019"
output: github_document
---

## Problem 1
* Section 1

```{r Question_one_part_one}
## load the tidyverse package
library(tidyverse)

## create data frame
df_one = tibble(
  ramdom_sample = rnorm(8),
  logical_vector = ramdom_sample > 0,
  character_vector = c(
  "CORONARY ARTERY DISEASE (CAD)",
  "STROKE",
  "LOWER RESPIRATORY INFECTIONS (LRI)",
  "CHRONIC OBSTRUCTIVE PULMONARY DISEASE (COPD)",
  "DIARRHEAL DISEASES",
  "HIV/AIDS",
  "RESPIRATORY CANCERS",
  "TUBERCULOSIS"
  ),
  factor_vector = factor(c(
  "severe",
  "moderate",
  "mild",
  "mild",
  "severe",
  "moderate",
  "moderate",
  "moderate"
  ))
)

## take the mean of each variable in the dataframe
ramdom_sample_mean = mean(pull(df_one, ramdom_sample))
logical_vector_mean = mean(pull(df_one, logical_vector))
character_vector_mean = mean(pull(df_one, character_vector))
factor_vector_mean = mean(pull(df_one, factor_vector))
```
### Observation: It worked only for ramdom_sample and logical_vector since both of them can be represented by numbers while character_vector and factor_vector can not be represented by numbers.



* Section 2

```{r Question_one_part_two, val = FALSE}
## convert the logical vector to numeric, and multiply the random sample by the result
as.numeric(pull(df_one, logical_vector))
product_rs_lv_numeric = pull(df_one, logical_vector) * 
  pull(df_one, ramdom_sample)
product_rs_lv_numeric

## convert the logical vector to a factor, and multiply the random sample by the result
as.factor(pull(df_one, logical_vector))
product_rs_lv_factor = pull(df_one, logical_vector) * 
  pull(df_one, ramdom_sample)
product_rs_lv_factor

## convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result
as.factor(pull(df_one, logical_vector))
as.numeric(pull(df_one, logical_vector))
product_rs_lv_n_f = pull(df_one, logical_vector) * 
  pull(df_one, ramdom_sample)
product_rs_lv_n_f
```


## Problem 2

```{r Question_two}
## load the tidyverse package
library(tidyverse)

## create data frame
df_two = tibble(
  x = rnorm(500),
  y = rnorm(500),
  logical_factor_two = x + y > 1
)

## change logical vector to numeric vector
logical_factor_two_numeric = as.numeric(pull(df_two, logical_factor_two))
logical_factor_two_numeric
## change logical vector to factor vector
logical_factor_two_factor = as.factor(pull(df_two, logical_factor_two))
logical_factor_two_factor
```
### a short description of the vector
*The size of the dataset is `r nrow(df_two)` by `r ncol(df_two)`
* The mean of the sample is `r mean(pull(df_two, x))`
* The median of the sample is `r median(pull(df_two, x))`
* The standard deviation of the sample is `r sd(pull(df_two, x))`
* the proportion of cases for which x + y > 1 is 
`r sum(pull(df_two, logical_factor_two), na.rm = TRUE)/500`

### scatterplot of y vs x
```{r}
library(tidyverse)
## scatterplot using the logical variable, blue(green) means the sum of x and y exceeds 1
ggplot(df_two, aes(color = logical_factor_two, x = x, y = y)) + 
  geom_point()
## scatterplot using the numeric variable, blue means the sum of x and y exceeds 1
ggplot(df_two, aes(color = logical_factor_two_numeric, x = x, y = y)) + 
  geom_point()
## scatterplot using the factor variable, blue(green) means the sum of x and y exceeds 1
ggplot(df_two, aes(color = logical_factor_two_factor, x = x, y = y)) + 
  geom_point()
## Export the first scatterplot to the project directory
ggsave("df_two.png")
```











